---
title: "Data preprocessing and summarization"
---

To ensure the accuracy of the Land Surface Temperature (LST) data, a histogram analysis was conducted. The histogram revealed a left-skewed distribution with a tail of small and unusual values. These values were likely outliers caused by unusual cold days during the summer or cloud effects. To maintain the integrity of the dataset, LST values below 20 degrees Celsius were removed. This data-cleansing process was necessary to eliminate potential outliers that could skew the data analysis.

```{r,echo=FALSE}
final_data = read.csv("final_data.csv")
```

```{r,message=FALSE,warning=FALSE}
library(tidyverse)


ggplot(final_data, aes(x = Lst)) +
  geom_histogram(binwidth = 0.5, fill = "#006400", color = "black") +
  geom_density(aes(y = ..count.. * 0.5), color = "blue", size = 1) +  
labs(x = "LST", y = "Frequency", title = "Histogram and Density of LST") +
  theme_minimal() +
  theme(plot.title = element_text(size = 20, face = "bold"),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 14))

```

In order to account for factors like the urban landscape of New York that can impact Land Surface Temperature, it was decided to employ a method of averaging LST values for each field every month during the summer months spanning from 2013 to 2022. Through this process, it is expected to achieve higher data accuracy. This improved dataset will facilitate more accurate statistical analyses and allow for more meaningful insights from the collected data.

```{r,warning=FALSE,message=FALSE}

library(dplyr)
summer_data = final_data |>
  filter(Lst>20) |>
  group_by(Date, Year, Month ) |>
  summarise_all(.funs = mean, na.rm = TRUE)  |>
  ungroup()

glimpse(summer_data)
```

```{r,echo=FALSE}
write.csv(summer_data[, -1], "summer_data.csv", row.names = FALSE)

```
