---
title: "Weather stations data"
---

In this seminar, relevant weather stations were classified and filtered from two GHCNd databases to obtain weather data.

The Global Historical Climatology Network Daily (GHCNd) is an online database of daily climate summaries from land surface monitoring stations worldwide. The database contains records from over 100,000 stations in 180 countries and territories, containing temperature, precipitation, snowfall, and snow depth data. (National Centers for Environmental Information. (n.d.))

Two databases were utilized containing the following data:

1.  **Stations**: Station ID, latitude, longitude, elevation, State (if applicable), and Station name.

2.  **Inventory**: Station ID, latitude, longitude, element type, and begin/end date.

After downloading data from the GHCNd website, it was converted from text to CSV format while selecting relevant columns.

```{r,warning=FALSE,message=FALSE}
library(dplyr)

data_stations <- read.table("ncei.noaa.gov_pub_data_ghcn_daily_ghcnd-stations.txt", header = FALSE, fill = TRUE, stringsAsFactors = FALSE)

station_data <- data_stations %>%
  select(V1, V2, V3) %>%
  setNames(c("Station_ID", "Latitude", "Longitude")) %>%
  as.data.frame()

station_data %>%
  write.csv("station_data.csv", row.names = FALSE)

```

```{r,warning=FALSE,message=FALSE}
library(dplyr)

data_inventory <- read.table("ncei.noaa.gov_pub_data_ghcn_daily_ghcnd-inventory.txt", stringsAsFactors = FALSE)

inventory_data <- data_inventory %>%
  select(V1, V2, V3, V4, V5, V6) %>%
  setNames(c("Station_ID", "Latitude", "Longitude", "Data_Type", "Start_Year", "End_Year")) %>%
  as.data.frame()

inventory_data %>%
  write.csv("Inventory_data.csv", row.names = FALSE)

```

In order to classify and filter relevant weather stations, two databases were utilized. It was important to select stations with temperature-averaged data, as the Landsat 8 LST values were extracted for each summer month's average values. Additionally, the selected stations had to collect data during summers from 2013 to 2022 and exist in 2013 when the Landsat 8 satellite was launched into space.

```{r,warning=FALSE,message=FALSE}
library(dplyr)

inventory_data <- read.csv("Inventory_Data.csv", stringsAsFactors = FALSE)
station_data <- read.csv("station_data.csv", stringsAsFactors = FALSE)

stations_with_data_in_2023 <- inventory_data %>%
  filter(Data_Type == "TAVG") %>%
  inner_join(station_data, by = "Station_ID") %>%
  mutate(Start_Year = as.numeric(Start_Year), End_Year = as.numeric(End_Year)) %>%
  filter(End_Year >= 2023, Start_Year < 2013)

stations_with_data_in_2023 %>%
write.csv("stations_with_data_in_2023.csv", row.names = FALSE)

```

Finally, the data frame containing all the necessary data.

```{r,warning=FALSE,message=FALSE}
stations_with_data_in_2023 = read.csv("stations_with_data_in_2023.csv")
glimpse(stations_with_data_in_2023)
```
