---
title: "Turf Fields Data"
---

The data presented in this chapter is sourced from a publication by the New York City Department of Parks & Recreation. The publication indicates that the majority of synthetic turf fields in NYC utilize crumb rubber infill made from repurposed car and truck tires. Additionally, a table is provided showcasing various athletic fields in New York that feature artificial turf grass. (New York City Department of Parks & Recreation. (n.d.))

```{r}
# Load data for New York Turf Fields 1
nyc1 <- read.csv("New York Turf Fields 1.csv")

# Display the first few rows of the dataset
head(nyc1)
```

Using Google Earth, I added longitude and latitude coordinates to each artificial turf grass field, as seen in the following table.

```{r, warning=FALSE, message=FALSE}
# Load data for New York Turf Fields 2
nyc2 <- read.csv("New York Turf Fields 2.csv")

# Display the first few rows of the dataset
head(nyc2)
```

To visualize the data, I created a map of the different artificial turf grass fields around New York.

```{r, warning=FALSE, message=FALSE}
library(leaflet)
library(dplyr)

# Create a leaflet map
leaflet(data = nyc2) %>%
  addTiles() %>%
  addMarkers(
    ~Longitude, ~Latitude,
    popup = ~paste("Location: ", Location, "<br>ID: ", ID)
  )
```
